---
title: "Interventions and SDG's"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

This page is based on the analysis conducted on Interventions and SDG's excel file.

***

## Dot Plot

Here is the first summary diagram I made. This dot-plot is a summary statistics, which just visually represents the results. I used abbreviated names to make it simpler.

A good way to understand this graph is to focus on the color. 

```{r eval=T, echo=F, message=F, warning=F}
source("code/int_2-dot_plot.r")
```
```{r eval=T, echo=F, fig.height=12, fig.width=6}
dot1
```
```{r eval=T, echo=F, fig.height=10, fig.width=6}
dot2
```

***

## Principle Component Analysis

**Disclaimer:** This is the first time doing a Principle Component Analysis, so I cannot guarentee the accuracy of these graphs. These graphs were prepared by following the instructions [here](http://rstudio-pubs-static.s3.amazonaws.com/53162_cd16ee63c24747459ccd180f69f07810.html).

I could not figure out the labels, so I would use the bottom graph to label the top graph in powerpoint.

```{r eval=T, echo=F, warning=F, message=F}
source("code/int_2-PCA.r")
```
```{r eval=T, echo=F}
no.label
```
```{r eval=T, echo=F}
yes.label
```