---
title: "HKH - Keyword Trend"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

## Keywords Trends

```{r eval=T, echo=F, warning=F, message=F}
source("code/syn_11-keyword_trends.r")
```
```{r eval=T, echo=F, warning=F, message=F}
#plot.simple
#plot.simple2
```

* Q1. Which line is better? Black line is the line graph. Blue line is the trend line which approximates all the values to create a smoother line.

* Q2. Since 2020 does not have complete value, the trend of 2020 will always be downwards. Suggestion is to remove 2020 from analysis.

```{r eval=T, echo=F, warning=F, message=F}
#plot.combine
```

* This is how to looks when you combine it all. For some there will be 3 lines.

```{r eval=T, echo=F, warning=F, message=F}
#plot.relative
```

* This is an attempt to keep relative % of keyword trends. I calculate relative trend by finding the proportion of each keyword with respect to the total number of keyword during that year. Let me know if this looks good or if this is too much noise. Each keyword will have 2 lines. While it looks more messy, it does help tell about the attribute of the keyword. 

***

## Update 2

Here are the two keywords I got to work on today. I still have to work on simplifying the axis and providing a legend for reference.

```{r eval=T, echo=F, message=F, warning=F}
#agroecology.plot
#agroecosystem.plot
```

## Update 3

```{r eval=T, echo=F, message=F, warning=F}
plot1
plot2
plot3
plot4
plot5
plot6
```
***



